---
title: "Title of My Final Project"
description: This is where I will describe my final project
site: bookdown::bookdown_site

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(tidyverse)
library(ggthemes)

```

```{r car-plot}
mtcars %>%
select(mpg, wt) %>%
ggplot(mapping = aes(x = wt, y= mpg))+
geom_point() +
geom_smooth(method= "lm", formula = y~x, se= FALSE)+
theme_clean()+
labs(title= "Fuel efficiency and weight",
subtitle="Heavier cars are less fuel efficient",
x="Weight(1000's of pounds)",
y="MPG")
```


<!--chapter:end:index.Rmd-->

---
title: "*About this site*"
description: "My name is **Bryan Li**"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## About Me
## About the project
This is title



## Goals
*I want to do good
  +*THis is not fun
  "This is data science"  
  ~Preceptor
  
  [Kanes Free High SChool Data Science Bootcamp(https://bootcamp.davidkane.info/)]

<!--chapter:end:about.Rmd-->

---
title: "Sources"
description: |
  An overview of sources used in my project.
author:
  - name: Nora Jones 
    url: https://example.com/norajones
    affiliation: Spacely Sprockets
    affiliation_url: https://example.com/spacelysprokets
date: "`r Sys.Date()`"
output: distill::distill_article
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

Distill is a publication format for scientific and technical writing, native to the web. 

Learn more about using Distill for R Markdown at <https://rstudio.github.io/distill>.

“This is where I will describe what sources I used and why I chose them. I may also discuss any broad challenges I faced while finding sources.” 







<!--chapter:end:sources.Rmd-->

